### 2015-08-03 usecase-combinatorial.tex
Name change spack-paper-sc15 -> spack-sc15
a few small tweaks

Spack presented a solution to both problems.  Package administrators can use Spack to
easily maintain a central install of {\tt gperftools} across combinations of
compilers and compiler versions.  Spack's {\tt gperftools} package also serves as a central
institutional knowledge repository, as its package files encode
the patches and configure lines required for each platform and compiler combination.
%
Figure~\ref{fig:gperftools} illustrates per-compiler and platform build rules with
a simplified version of the install routine for {\tt gperftools}.
%(the full {\tt gperftools} install routine includes other compilers and more options).
The package applies a patch if {\tt gperftools} 2.4 is built with the XL compiler,
and it selects the correct configure line based on the spec's platform and compiler.

LC's {\tt mpileaks} tool, which has been a running example in this paper,
has an even larger configuration space than {\tt gperftools}.  It must be built
for different compilers, compiler versions, MPI implementations, and MPI
versions. As with {\tt gperftools}, we have been able to install many different
configurations of {\tt mpileaks} using Spack.  Moreover, Spack's virtual dependency 
system allows us to quickly compose a new {\tt mpileaks} build when a new MPI library is 
deployed at LC, {\it without} modifying the {\tt mpileaks} package itself.
%Though we simplified its dependency structure
%here, the {\tt callpath} library can be built with three different stack trace libraries:
%{\tt dyninst}, {\tt libunwind}, or {\tt glibc}.  For some codes we may soon need to build
%different versions of {\tt mpileaks} with different {\tt callpath} configurations.

>>>>

Spack presented a solution to both problems.  Package administrators can use Spack to
maintain a central install of {\tt gperftools} across combinations of
compilers and compiler versions easily.  Spack's {\tt gperftools} package 
also serves as a central
institutional knowledge repository, as its package files encode
the patches and configure lines required for each platform and compiler combination.
%
Figure~\ref{fig:gperftools} illustrates per-compiler and platform build rules with
a simplified version of the install routine for {\tt gperftools}.
%(the full {\tt gperftools} install routine includes other compilers and more options).
The package applies a patch if {\tt gperftools} 2.4 is built with the XL compiler,
and it selects the correct configure line based on the spec's platform and compiler.

LC's {\tt mpileaks} tool, which has been a running example in this paper,
has an even larger configuration space than {\tt gperftools}.  It must be built
for different compilers, compiler versions, MPI implementations, and MPI
versions. As with {\tt gperftools}, we have been able to install many different
configurations of {\tt mpileaks} using Spack.  Moreover, Spack's virtual dependency
system allows us to compose a new {\tt mpileaks} build quickly when a new MPI library is
deployed at LC, {\it without} modifying the {\tt mpileaks} package itself.
%Though we simplified its dependency structure
%here, the {\tt callpath} library can be built with three different stack trace libraries:
%{\tt dyninst}, {\tt libunwind}, or {\tt glibc}.  For some codes we may soon need to build
%different versions of {\tt mpileaks} with different {\tt callpath} configurations.
